Experiment 2b: Analysis of Embedded Questions, NoContext

### 2021-11-11 analysis/06_experiment/rscripts/graphs.Rmd
added initial files from old repo

---
title: "Graphs for Experiment 03, Embedded Questions Corpus Study"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

@@

# Read in data
```{r import data}
# Read database
corp = read.table("../../../corpus/results/swbd.tab",sep="\t",header=T,quote="")
# Read experimental data in
d = read.csv("../data/normed.csv")
nrow(d) # 174549

@@

# join dfs together
d <- left_join(d, corp_match, by="tgrep_id")

@@

## Mean Rating
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in mean_rating
ggplot(data = agr, aes(x = mean_rating, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  # facet_grid(~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/ex1b_denisty_mean_ratings.pdf",width=6,height=3)
```

## Standard Deviation
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in SD 
ggplot(data = agr, aes(x = sd, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/ex1b_denisty_sd.pdf",width=6,height=3)
```

@@

## Overall
```{r}
agr = d %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

dodge = position_dodge(.9)
ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  ylim(0,.6) +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/overall_noSQ.pdf",width=2,height=2)
```

## Graph Interaction between Modal and Wh
```{r}

@@

# ggsave("../graphs/modxwh_noSQ.pdf",width=3,height=4)
```

## Look at just Wh
```{r}
agr = d %>%
  group_by(paraphrase,Wh) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()
# Re-Order the WH-levels by overall composition of DB
agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))
ggplot(agr,aes(x=Wh, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9))  +
  # ggtitle("Mean rating for Wh-Word") +
  xlab("Wh-Word") +
  ylab("Mean rating") +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/final_normed_wh.pdf")
```

## Look at just ModalPresent
```{r}
agr = d %>%
  group_by(paraphrase,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=ModalPresent, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  xlab("Modal Present") +
  ylab("Mean rating") +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# legend.spacing.y = unit(-10, 'cm'))
# guides(fill=guide_legend(title="Paraphrase"))
# ggsave("../graphs/final_normed_modalpresent.pdf")

@@

## Graph MatrixVerb only
```{r}
verb_count = d %>%
  group_by(VerbLemma) %>%
  summarize(count = n())

@@

surp = subset(d,d$VerbLemma == "surprise")
nrow(surp)
agr = d %>%
  # Most frequent
  filter(VerbLemma %in% c("know","see","wonder","understand","be","understand","surprise","tell","figure","say","think","sure","learn","remember")) %>%
  group_by(paraphrase,VerbLemma,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

# Graph individual verbs
```{r }
agr = d %>%
  filter(VerbLemma == "know") %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

```{r Looking at individual items}
the_high = d %>%
  filter((paraphrase == "the")) %>% #  & (Wh == "why")
  group_by(tgrep_id,Sentence) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  filter(mean_rating > .5) %>%
  View()

a_high = d %>%
  filter((paraphrase == "a")) %>% #
  group_by(tgrep_id,Sentence, Question) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  # filter(mean_rating > .3) %>%
  View()

all_high = d %>%
  filter(paraphrase %in% c("every")) %>% 
  group_by(tgrep_id,Sentence) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  filter(mean_rating > .1) %>%
  View()

# Look at all ratings for a specific example
ex = test %>%
  filter(tgrep_id == "29177:41") %>%
  select(Sentence,Question,paraphrase,rating) %>%
  group_by(Sentence,Question,paraphrase) %>%
  summarize(mean_rating = mean(rating), sd = sd(rating)) %>%
  View()

@@

ex = test %>%
  filter(tgrep_id == "39551:19")
View(ex[,c("SentenceParse")])
```
(TOP (S (CC and) 
        (NP-SBJ-2 (PRP I)) 
        (VP (VBP have) 
            (VP (VBN been) 
                (VP (VBG debating) (SBAR (WHNP-1 (WP what)) (S (NP-SBJ (-NONE- *-2)) (VP (TO to) (VP (VB cook) (NP (-NONE- *T*-1)))))) (SBAR-PRP (IN because) (S (NP-SBJ (NP (CD one)) (PP (IN of) (NP (PRP$ my) (NNS guests)))) (VP (VBZ is) (NP-PRD (DT a) (NN vegetarian)))))))) (. .) (-DFL- E_S)))

>>>>

---
title: "Graphs for Experiment 06, Embedded Questions NoContext Corpus Study"
author: Morgan Moyer
date: May 18, 2021
output: html_document
---

@@

```{r import data}
# Read database
corp = read.table("../../../corpus/results/swbd.tab",sep="\t",header=T,quote="")
# Read experimental data in
d = read.csv("../data/normed_nocontext_embedded.csv")

@@

# join dfs together
d <- left_join(d, corp_match, by="tgrep_id")
```

@@

## Mean Rating
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in mean_rating
ggplot(data = agr, aes(x = mean_rating, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  # facet_grid(~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/ex2b_denisty_mean_ratings.pdf",width=6,height=3)
```

## Standard Deviation
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in SD 
ggplot(data = agr, aes(x = sd, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/ex2b_denisty_sd.pdf",width=6,height=3)
```

@@

## Overall

```{r Graph normed data Overall}
agr = d %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

View(agr)

dodge = position_dodge(.9)
ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  ylim(0,.6) +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/overall_nocontext_embedded.pdf",width=2,height=2)
```

## Modal x Wh-Word

```{r Look at Interaction between Modal and Wh}

@@

# ggsave("../graphs/modxwh_nocontext_embedded.pdf",width=3,height=4)
```

```{r Look at just Wh,include=FALSE}
agr = d %>%
  group_by(paraphrase,Wh) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()
# Re-Order the WH-levels by overall composition of DB
agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))
ggplot(agr,aes(x=Wh, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9))  +
  # ggtitle("Mean rating for Wh-Word") +
  xlab("Wh-Word") +
  ylab("Mean rating") +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
```

```{r Look at just ModalPresent,include=FALSE}
agr = d %>%
  group_by(paraphrase,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=ModalPresent, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  xlab("Modal Present") +
  ylab("Mean rating") +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)

@@

```{r Graph MatrixVerb only}
verb_count = d %>%
  filter(grepl("experiment_06",proliferate.condition)) %>%
  group_by(VerbLemma) %>%
  summarize(count = n())

@@

agr = d %>%
  # Most frequent
  filter(VerbLemma %in% c("know","see","wonder","understand","be","understand","surprise","tell","figure","say","think","sure","learn","remember")) %>%
  group_by(paraphrase,VerbLemma,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

```{r Look at individual verbs}
agr = d %>%
  filter(VerbLemma == "know") %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

```{r Looking at individual items}
the_high = d %>%
  filter((paraphrase == "the") & (VerbLemma == "surprise")) %>% #  & (Wh == "why")
  group_by(tgrep_id,Sentence) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  filter(mean_rating > .5) %>%
  View()

a_high = d %>%
  filter((paraphrase == "a") & (VerbLemma == "tell")) %>% #     & (ModalPresent == "no") & (Wh == "who")
  group_by(tgrep_id,Sentence, Question) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  # filter(mean_rating > .3) %>%
  View()

all_high = d %>%
  filter((paraphrase %in% c("every") & VerbLemma == "predict")) %>% #  & (Wh == "when") & (ModalPresent == "yes")
  group_by(tgrep_id,Sentence) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  filter(mean_rating > .1) %>%
  View()

# Look at all ratings for a specific example
ex = d %>%
  filter(tgrep_id == "29177:41") %>%
  select(Sentence,Question,paraphrase,rating) %>%
  group_by(Sentence,Question,paraphrase) %>%
  summarize(mean_rating = mean(rating), sd = sd(rating)) %>%
  View()

@@

ex = d %>%
  filter(tgrep_id == "39551:19")

### 2021-11-11 analysis/06_experiment/rscripts/main_analysis.Rmd
added initial files from old repo

---
title: "Experiment 1b: Analysis of Embedded Questions, Context"
author: "mcmoyer"
date: "March 30, 2021"
---

@@

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d = read.csv("../data/normed.csv")
d$ModalPresent = as.factor(d$ModalPresent)
d$Wh = as.factor(d $Wh)
d$paraphrase = as.factor(d$paraphrase)
d$VerbLemma = as.factor(d$VerbLemma)
```

# Is rating modulared by Paraphrase (MS/MA), Wh and ModalPresent?
- No significant three-way interactions

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d.ms.ma = d %>%
  filter(paraphrase %in% c("a","every")) %>%
  # hand-code paraphrase so mean-centering is more interpretatble 
  # (otherwise, "every" will be 1 and "a" will be 0 by default)
  mutate(paraphrase.dc = recode(paraphrase, "a" = 1, "every" = 0) ) %>%
  # mean-center
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

@@

```{r}

# m.ms.ma.full = lmer(normed_rating ~ cParaphrase*Wh*cModalPresent + (1+cParaphrase+Wh+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma.full, "model-msma-full.rds")

@@

# Other Models
## Does paraphrase predict rating?
- No

```{r}
# m.ms.ma = lmer(normed_rating ~ cParaphrase + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id) + (1+cParaphrase|VerbLemma), data=d.ms.ma)
# saveRDS(m.ms.ma, "model-msma.rds")

m.ms.ma <- readRDS("model-msma.rds")
summary(m.ms.ma)
# confint(m.ms.ma)
# cParaphrase -0.09734602 -0.03875422
```

## Are MS ratings modulated by linguistic form factors?
- no interaction between Wh-Word and Modality
- modal questions increase rating
- but compared to 'when', all other 'wh'-words decrease ratings
```{r}
d.ms = d %>% 
  filter(paraphrase=="a") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

@@

m.ms <- readRDS("model-ms.rds")
summary(m.ms)
# confint(m.ms)
```

## Are know-wh questions MA-biased?
```{r}
d.ms.ma.know = d.ms.ma %>% 
  filter(VerbLemma == "know") %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms.ma.know$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))
```

@@

m.know <- readRDS("m-know.rds")
summary(m.know)
```
## Know-What
```{r know-what}
d_what_know = d.ms.ma.know %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

@@

# Are MA ratings modulated by linguistic form factors?
- some differences based on WH-word, both 'who' and 'how' increase MA ratings compared to 'when'
```{r}
d.ma = d %>% 
  filter(paraphrase=="every") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

# m.ma = lmer(normed_rating ~ cModalPresent*Wh + (1+Wh+cModalPresent|workerid) + (1|VerbLemma) + (1|tgrep_id), data=d.ma)
# saveRDS(m.ma, "model-ma.rds")

m.ma <- readRDS("model-ma.rds")
summary(m.ma)
# confint(m.ma)
```

# Full Model with all three paraphrases

```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# No three-way interactions
contrasts(d$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

@@

```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# m.full = lmer(normed_rating ~ cModalPresent*Wh*paraphrase + (1+paraphrase+Wh+cModalPresent|workerid) + (1+paraphrase|VerbLemma) + (1+paraphrase|tgrep_id), data=centered,REML=FALSE) 
# saveRDS(m.full, "EQ-model-full-mvRE.rds")
m.full <- readRDS("EQ-model-full-mvRE.rds")
summary(m.full)
```

>>>>

---
title: "Experiment 2b: Analysis of Embedded Questions, NoContext"
author: "mcmoyer"
date: "March 30, 2021"
output: html_document
---

@@

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d = read.csv("../data/normed_nocontext_embedded.csv")

d$ModalPresent = as.factor(d$ModalPresent)
d$Wh = as.factor(d $Wh)
d$paraphrase = as.factor(d$paraphrase)
d$VerbLemma = as.factor(d$VerbLemma)

@@

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d.ms.ma = d %>%
  filter(paraphrase %in% c("a","every")) %>%
  # hand-code paraphrase so mean-centering is more interpretatble 
  # (otherwise, "every" will be 1 and "a" will be 0 by default)
  mutate(paraphrase.dc = recode(paraphrase, "a" = 1, "every" = 0) ) %>%
  # mean-center
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))
```

# Is rating modulated by Paraphrase, Wh and ModalPresent?

```{r}
# m.ms.ma.full = lmer(normed_rating ~ cParaphrase*Wh*cModalPresent + (1+cParaphrase+Wh+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma.full, "model-msma-full.rds")

@@

# Is there an overall bias for MA? Does paraphrase predict the rating?
- No, but bias for MS
```{r}
# m.ms.ma = lmer(normed_rating ~ cParaphrase + (1+cParaphrase|workerid) + (1+cParaphrase|VerbLemma) + (1+cParaphrase|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma, "model-msma.rds")

m.ms.ma <- readRDS("model-msma.rds")
summary(m.ms.ma)
```

# Are MS ratings modulated by linguistic form factors?
- No 2-way interactions
- but significant effects both of Wh-Word and ModalPresent
  - Modal increases ratings
  - compared to 'when' all others lead to a decrease in ratings
```{r}
d.ms = d %>% 
  filter(paraphrase=="a") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

@@

m.ms <- readRDS("model-ms.rds")
summary(m.ms)

# Are MA ratings modulated by linguistic form factors?
- not at all
```{r}
d.ma = d %>% 
  filter(paraphrase=="every") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

# m.ma = lmer(normed_rating ~ cModalPresent*Wh + (1+Wh+cModalPresent|workerid) + (1|tgrep_id) + (1|VerbLemma), data=d.ma)
# saveRDS(m.ma, "model-ma.rds")

m.ma <- readRDS("model-ma.rds")
summary(m.ma)
```

# Are know-wh questions MA-biased?
```{r}
d.ms.ma.know = d.ms.ma %>% 
  filter(VerbLemma == "know") %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms.ma.know$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))
```

@@

m.know <- readRDS("m-know.rds")
summary(m.know)
```

## Know-What
```{r know-what}
d_what_know = d.ms.ma.know %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

@@

# Other Models
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# Set the reference levels
contrasts(d$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

@@

## Full Model with all paraphrases
- no significant 3-way interactions
- some 2-way interactions: only between paraphrase and Wh (how vs when, a vs every; why vs when, the versus every
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# m.full = lmer(normed_rating ~ cModalPresent*Wh*paraphrase + (1+paraphrase+Wh+cModalPresent|workerid) + (1+paraphrase|VerbLemma) + (1+paraphrase|tgrep_id), data=centered,REML=FALSE)
# saveRDS(m.full, "model-nocontext-embedded-full-rMV.rds")

nocontext_model <- readRDS("model-nocontext-embedded-full-rMV.rds")
summary(nocontext_model)
```
